Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-01-29 vesicle_code/docs/adhesion/adhesion.tex
started fixing up the extensional section ... needs work yet on the language

As expected, we observe two different regimes---the extensional rate is
sufficiently small that the doublet structure is not broken, and the
extensional rate is sufficiently large that the doublet is broken.  In
Figure~\ref{fig:extensionalPhaseDiagram}.

@@

In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, we show
snapshots of two vesicles of reduced area $0.70$ in an extensional flow
with three different extensional rates.  Interestingly, when the
extensional rate does not overcome the adhesion rate, the doublet does
not remain parallel to the stagnation point, but instead tilts to an
inclination angle (Figures~\ref{fig:extensional1}
and~\ref{fig:extensional2}.  We include a plot of the inclination angle
as a function of time for varying extensional rates (left plot of
Figure~\ref{fig:extensionalInclinationAngle}).  The inclination angle is
defined defined in with respect to the diverging direction (right plot
of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
broken at reduced area $0.70$, the extensional rate is sufficiently
large to align the long axis of the vesicle with the diverging direction
and then the vesicles separate.  However, for larger reduced areas, the
separation dynamics is different.  Instead, the vesicles tilt to an
inclination angle and then separate (Figure~\ref{fig:extensional4}).

@@

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.1$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

@@

@@

In our formulation we did not include any electrostatic interactions between membranes under adhesion. When the electrostatic interaction is important, an electro-osmotic pressure
in the thin film is found to be responsible for the observed membrane undulation \cite{LiraDimova}.

>>>>

As expected, we observe two different regimes---the extensional rate is
sufficiently small that the doublet structure is not broken, and the
extensional rate is sufficiently large that the doublet is broken.  In
Figure~\ref{fig:extensionalPhaseDiagram}, the red marks correspond to
parameters where the doublet is broken while the red marks correspond to
parameters where the doublet tends to a steady-state fluid trap.  In the
case that there is a fluid trap, the doublet rotates from the unstable
configuration where the converging rate is in the direction that is
parallel to the long axis of the vesicles.  At low extensional rates,
the inclination angle approaches $\pi$ which corresponds to the
converging direction being aligned with the short axis of the vesicle
(Figure~\ref{fig:extensional1}).  As the extensional rate is increased,
the vesicle tilts to a shallower inclination angle
(Figures~\ref{fig:extensional2} and~\ref{fig:extensional3}).  Finally,
when the inclination angle is sufficiently large, the doublet is broken
(Figure~\ref{fig:extensional4}).  In
Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round marks
correspond to the inclination angle.  The square marks correspond to
doublets that do not reach a steady-state inclination angle in the given
time horizon.

@@

%In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, we show
%snapshots of two vesicles of reduced area $0.70$ in an extensional flow
%with three different extensional rates.  Interestingly, when the
%extensional rate does not overcome the adhesion rate, the doublet does
%not remain parallel to the stagnation point, but instead tilts to an
%inclination angle (Figures~\ref{fig:extensional1}
%and~\ref{fig:extensional2}.

@@

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.1$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

@@

We include a plot of the inclination angle as a function of time for
varying extensional rates (left plot of
Figure~\ref{fig:extensionalInclinationAngle}).  The inclination angle is
defined defined in with respect to the diverging direction (right plot
of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
broken at reduced area $0.70$, the extensional rate is sufficiently
large to align the long axis of the vesicle with the diverging direction
and then the vesicles separate.  However, for larger reduced areas, the
separation dynamics is different.  Instead, the vesicles tilt to an
inclination angle and then separate (Figure~\ref{fig:extensional4}).

@@

In our formulation we did not include any electrostatic interactions
between membranes under adhesion. When the electrostatic interaction is
important, an electro-osmotic pressure in the thin film is found to be
responsible for the observed membrane undulation~\cite{LiraDimova}.
